Figures

### 2023-10-26 output/paper/figures.qmd
Modofied code to plot results of weights and marginal effects. Saving them to file too.

---
title: "Figures"

format:
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers

link-citations: true
linkcolor: blue

editor_options: 
  chunk_output_type: console

execute:
  echo: false
  warning: false
  error: false
  message: false
---

- Number figures according to the order in which they are first mentioned in the main text.
- Clearly label all axes, giving both the measure and the unit of measurement.
- Not larger than 7.5 inches in width.
- Save and submit each main text figure as an individual file (PDF with fonts embedded). Include the figure number in the file name of each figure.
- Provide main text figure captions on a new page of the main text after the tables.
- Provide the title for each figure below the figure on the same manuscript page as the figure itself.
- Include a title for the entire figure and descriptors for each panel.

>>>>

---
title: "Figures"
format:
  pdf:
    pdf-engine: lualatex
    number-sections: true
    toc: false
    include-in-header:
      text: |
        \usepackage{lineno}
        \usepackage{rotating}
        \usepackage{float}
        \usepackage{typearea}
    include-before-body:
      text: |
        \linenumbers
link-citations: true
linkcolor: blue
editor_options: 
  chunk_output_type: console
execute:
  echo: false
  warning: false
  error: false
  message: false
---

- Number figures according to the order in which they are first mentioned in the main text.
- Clearly label all axes, giving both the measure and the unit of measurement.
- Smallest type size: 8pt.
- Maximum width: 7 inches in portrait, 9 inches in landscape mode.
- Multi-panel figures: capital letters followed by closing parenthesis, completely above and to the left of the panel.
- Use log-scale when plotting relative measures of effects.
- Figure titles and legends should be submitted as single paragraph.
- The text of figure legends typed after the reference list.
- Save and submit each main text figure as an individual file (PDF with fonts embedded).
